---
title: "Group 8 - Lab 6"
author: "David Wiley"
date: "February 16, 2019"
output: pdf_document
---

## Problem 2.11

Consider the weight and blood pressure data in Problem 2.10. Fit a no -
intercept model to the data and compare it to the model obtained in Problem
2.10. Which model would you conclude is superior?


```{r}

# Reading in the information for Weight and Symbolic BP
dat=read.csv("C:\\Users\\Nick\\Documents\\0_Spring 2019\\Applied Regression\\Labs_HW\\Data_Sets\\Chapter 2\\Problems\\data-prob-2-10.csv", header = T)
y = dat[,2]
x = dat[,1]
n = length(x)

# Calculating variables
Sxx = sum(x^2) - sum(x)^2 / n
Sxy = sum(x*y) - sum(x)*sum(y) / n

B1H = Sxy / Sxx
B0H = mean(y) - mean(x)*B1H

yH = B0H + sort(x) * B1H

SSr = B1H * Sxy
SSres = sum((y - mean(y))^2) - SSr
  
SSt = SSr + SSres
MSres = SSres / (n-2)

seB1H = sqrt(MSres/Sxx)
seB0H = sqrt(MSres * (1 / n + mean(x)^2 / Sxx))

MSr = SSr/1

F0 = MSr / MSres


# Estimating the correlation coefficient
r = Sxy / sqrt(Sxx * SSt)
r
R2 = SSr / SSt
R2

summary(lm(y~x))

```

## Interpretation of first model:

The MSE for the first model is $```r R2```$.

### Setting up the no-intercept model:

```{r}

summary(lm(y~x-1))
MSE2 = 12.6^2

```

## Interpretation:

Comparing the two models we can see: 

### The model with no intercept:
$$\hat{y}=0.792x$$
With an MSE of $```r MSE2```$.

### The model with an intercept:
$$\hat{y}=```r B0H```+```r B1H```*x$$ 
with an MSE of $```r R2```$.

The test on $\hat{\beta}_{0}$ is significant. Therefore, the first model would be the better of the two to use.
