---
title: "TruongDuy 1.23.19"
author: "Duy Truong"
date: "January 23, 2019"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
$ \hat{y} = b_0 + b_1x $


```{r, echo = FALSE}
purity <- read.csv("C:\\Users\\Sundas Mohi-Truong\\Documents\\UHD\\SPRING 2019\\LinRegression\\Data Sets\\Chapter 2\\Problems\\data-prob-2-7.csv", header = TRUE)

```


PROBLEM 1 :

Using the purity data from Problem 2.7, calculate the estimates for the true slopes and true intercept using RMarkdown



```{r, echo=FALSE}
## Set-Up
yi = purity$hydro
xi = purity$purity
n=length(purity$hydro)
  
Sxy <- sum(yi*xi) - ((sum(yi)*sum(xi))/n)
Sxx <- sxx <- sum(xi^2) - ((sum(xi))^2 / n)
B1 <- Sxy/Sxx

print(B1)

Bo <- mean(yi) - B1*mean(xi)
print(Bo)


```

PROBLEM 2: 

Calculate the estimate of the true error variance. Interpret


```{r, echo=FALSE}
## Residual /Error Sum of Squares/Estimator
SSres <- sum((yi-mean(yi))^2) - B1*Sxy
MSres = SSres/(n-2)
print(MSres)

## The smaller our MSres is the more reliable our data is since there is less variability
```


The smaller our MSres is the more reliable our data is since there is less variability



PROBLEM 3:

Plot the data and the fitted simple linear regression line in one graph

```{r, echo = FALSE}
## Plotting

plot(xi,yi,ylab = 'Hydro', xlab = 'Purity', main = "Purity vs Hydro", sub = "Duy Truong")
# print(lm(yi~xi,purity))
abline(Bo,B1, lwd = 2, col='blue')
```

PROBLEM 4:

Verify (using R) Properties 1,2,4 and 5 of the least squares fit

```{r, echo = FALSE}
## Verification
yHat = Bo+B1*xi
ei = yi - yHat
sum(yi-yHat)
P1 <- sum(yi-yHat) == sum(ei)
P2 <- round(sum(yi)) == round(sum(yHat))
P4 <- (sum(xi*ei))
P5 <- (sum(yHat*ei))
Verify = data.frame(P1,P2,P4,P5)
Verify
```


HOMEWORK 2:

```{r, echo=FALSE}
#######################
# T-Stat / Hypothesis 
#######################
seB1h <- sqrt(MSres/Sxx)
tstat1 = (B1/seB1h)
tstat1 

#two-sided P-value Approach
pval01 <- 2*pt(-abs(tstat1), df=n-2)
pval01

#### ANOVA
SSr = sum((yHat - mean(yi))^2)
MSr = SSr/1
SSt = SSr+SSres
F0 = MSr/MSres
F0
pf(F0, df1 =1, df2 = n-2, lower.tail=FALSE)

anova(lm(yi~xi,purity))
```

