---
title: "TruongWileyHW5"
author: "Duy Truong"
date: "February 6, 2019"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

dat <- read.csv("C:\\Users\\Sundas Mohi-Truong\\Documents\\UHD\\SPRING 2019\\LinRegression\\Data Sets\\Chapter 2\\Problems\\data-prob-2-12.csv", header = TRUE)
```

The number of pounds of steam used per month at a plant is thought to be
related to the average monthly ambient temperature. The past year ’ s usages
and temperatures follow

```{r, echo = FALSE}
xi <- dat$temp
yi <- dat$usage
n=length(xi)
fit = lm(yi~xi)
summary(fit)

Sxx=sum(xi^2)-sum(xi)^2/n
Sxy=sum(xi*yi)-sum(xi)*sum(yi)/n

B1H = Sxy/ Sxx
B0H = mean(yi)-mean(xi)*B1H


yH=B0H + sort(xi)*B1H

res = yi- (B0H + xi*B1H)
SSres = sum(res^2)
MSres = SSres/(n-2)

seB0H = sqrt(MSres*( 1/n + mean(xi)^2/Sxx ) )
seB1H = sqrt(MSres/Sxx)
tstat0 = (B0H-0)/seB0H
tstat1 = (B1H-0)/seB1H

#ANOVA
SSr= sum( (yH-mean(yi))^2 )
MSr= SSr/1
SSt= SSr+SSres
F0=MSr/MSres

#R^2 = proportion of variation in yi explained by xi
SSr/SSt
1-SSres/SSt

#P-value Calculations for t(alp/2,n-2)
2*pt(tstat0, df=n-2, lower.tail = FALSE)
#p-value for t(alp/2,n-1)
2*pt(tstat1, df=n-2, lower.tail = FALSE)

pf(F0, 1,n-2, lower.tail = FALSE)

anova(fit)
confint(fit)
```

2.12a - Fit a simple linear regression model to the data.
```{r}
plot(xi,yi)
lines(sort(xi),yH, col="red")
```
By looking at our regression line against the plot, we can see that it fits well.

2.12b - Test for significance of regression.

```{r, echo = FALSE}
print(MSres)
```
Our MSres is relatively a small number, interpretting this, we can conclude that our linear fit has low variability, therefore the fit is accurate.


2.12c - Plant management believes that an increase in average ambient temperature of 1 degree will increase average monthly steam consumption by
10,000 lb. Do the data support this statement?

```{r, echo = FALSE}
alpha=0.1
B1H - qt(1-alpha/2, n-2)*seB1H
B1H + qt(1-alpha/2, n-2)*seB1H
```
The data does not support this statement with a 90% interval the increase does not include the expected 10,000.


2.12d - Construct a 99% prediction interval on steam usage in a month with
average ambient temperature of 58 ° 

```{r, echo = FALSE}
xo=58
alp = 0.01
y_est=B0H + B1H*xo

#Lower
lower = y_est-qt(1-alp/2, n-2)*sqrt( MSres*(1+1/n + (xo-mean(xi))^2 )/Sxx )
lower
#Upper
upper = y_est+qt(1-alp/2, n-2)*sqrt( MSres*(1 + 1/n + (xo-mean(xi))^2 )/Sxx )
upper
```
If the ambient temperature of the plant is 58 degrees we are 99% confident that the amount of steam usage would be between 526521 and 528997 pounts.


